Figures and Analysis for 2023 Manuscript

### 2023-10-19 data-raw/Manuscript2023_Workflow.Rmd
Minor descriptors added to workflow document

pl5A <- all_my_data %>%
  filter(Detect %in% TRUE,
         exclude %in% FALSE,
         Dose > 0) %>%
  group_by(Chemical,
           Species,
           Reference,
           Route, 
           Media,
           Dose, Time) %>%
  filter(n() > 1,
         sum(is.na(Conc)) != n(),
         LOQ < Conc) %>%
  mutate(meanConc = mean(Conc, na.rm = TRUE)) %>%
  ungroup() %>%
  rowwise() %>%
  mutate(foldConc = Conc / meanConc) %>%
  ggplot(aes(x = foldConc)) +
  geom_histogram(binwidth = 0.2,
                 fill = "grey5",
                 color = "grey5",
                 linewidth = 0.4) +
  coord_cartesian(xlim =  c(0, 4),
                  ylim = c(0, 4000)) +
  scale_y_continuous(expand = c(0, 0),
                     breaks = c(0, 1000, 2000, 3000),
                     labels = c("0", "1", "2", "3")) +
  expand_limits(y = 0) +
  geom_vline(xintercept = c(0.5, 2), color = "red3", linetype = "dashed") +
  theme_classic() +
  labs(x = "Mean-normalized\nconcentration",
                y = "Observations\n(thousands)") +
  theme(text = element_text(size = 10),
        panel.border = element_rect(color = "black", linewidth = 1, fill = NA),
        panel.background = element_blank(),
        panel.grid.major.y = element_line(color = "grey90", linewidth = 0.4),
        axis.title = element_text(face = "bold"),
        axis.line = element_blank(),
        plot.background = element_blank(),
        axis.ticks.y = element_blank())

>>>>

pl5A <- all_my_data %>%
  filter(Detect %in% TRUE,
         exclude %in% FALSE,
         Dose > 0) %>%
  group_by(Chemical,
           Species,
           Reference,
           Route, 
           Media,
           Dose, Time) %>%
  filter(n() > 1,
         sum(is.na(Conc)) != n(),
         LOQ < Conc) %>%
  mutate(meanConc = mean(Conc, na.rm = TRUE)) %>%
  ungroup() %>%
  rowwise() %>%
  mutate(foldConc = Conc / meanConc) %>%
  # Plotting
  ggplot(aes(x = foldConc)) +
  geom_histogram(binwidth = 0.2,
                 fill = "grey5",
                 color = "grey5",
                 linewidth = 0.4) +
  coord_cartesian(xlim =  c(0, 4),
                  ylim = c(0, 4000)) +
  scale_y_continuous(expand = c(0, 0),
                     breaks = c(0, 1000, 2000, 3000),
                     labels = c("0", "1", "2", "3")) +
  expand_limits(y = 0) +
  geom_vline(xintercept = c(0.5, 2), color = "red3", linetype = "dashed") +
  theme_classic() +
  labs(x = "Mean-normalized\nconcentration",
                y = "Observations\n(thousands)") +
  theme(text = element_text(size = 10),
        panel.border = element_rect(color = "black", linewidth = 1, fill = NA),
        panel.background = element_blank(),
        panel.grid.major.y = element_line(color = "grey90", linewidth = 0.4),
        axis.title = element_text(face = "bold"),
        axis.line = element_blank(),
        plot.background = element_blank(),
        axis.ticks.y = element_blank())

pl5A
